Untitled

### 2020-12-09 Manuscript/Manuscript_Paper.Rmd
Update Manuscript_Paper.Rmd

---
title: "Untitled"
author: "Kimberly Hinz"
date: "2020/12/08"
output:
  word_document:
    reference_docx: Styles1.docx
    fig_caption: true
    # toc: true
    # toc_depth: 5
bibliography: References.bib
csl: IJSEM.csl
---

\newpage
# Abstract
*Mixta* is a recently described genus within the bacterial family *Erwiniaceae* that is closely related to *Pantoea*, *Erwinia*, and *Tatumella*. Depending on the genes and method used for phylogenetic analysis, the genus with which *Mixta* shares the most recent ancestor differs. This study aimed to determine the cause behind these contentious results, and identified genes that may have resulted from horizontal gene transfer. Ten complete or partial genomes – two *Mixta* species, six species from other *Erwiniaceae* genera, and two outgroups – were retrieved from NCBI and annotated. Homologous genes were extracted yielding a dataset of 799 genes. The genes were aligned With the ClustalW algorithm and MEGA-CC was used for model testing and computing phylogenetic trees for each gene for both nucleotide and amino acid sequences. Distance matrices were then extracted from these trees. Nucleotide and amino acid identity analyses were also done in `R` programming language. *Pantoea* was the closest relative to the *Mixta* species in most of the analyses; however, results were not consistent across analyses. Some genes were also found to be more similar to other, non-*Pantoea* species. Diligence must be given to the selection of genes for phylogenetic analysis and to the method chosen to prevent xenologous signal from distorting the true relationships. Furthermore, future research should consider that different phylogenetic analyses may give different results.

@@

```{r echo = FALSE, message = FALSE, fig.cap=TRUE}
strain <- data.frame(Species = c("Mixta calida", "Mixta gaviniae", "Pantoea agglomerans", "Pantoea septica", "Erwinia amylovora",
                                 "Erwinia tasmaniensis", "Tatumella ptyseos", "Tatumella saanichensis", 
                                 "Enterobacter cloacae subsp cloacae", "Pseudomonas syringae pv syringae"),
                     Strain = c("DSM_22759", "DSM_22758", "NBRC_102470", "LMG_5345", "CFBP_1232", "ET1/99", "NCTC_11468",
                                "NML_06-3099", "ATCC_13047", "ICMP_3023"),
                     `GenBank Accession No.` = c("GCA_002953215.1", "GCA_002953195.1", "GCA_001598475.1", "GCA_002095575.1", "GCA_000367625.2",
                                                 "GCA_000026185.1", "GCA_900478715.1", "GCA_000439375.1", "GCA_000025565.1", "GCA_001401075.1"),
                     Level = c("complete genome", "complete genome", "contigs", "contigs", "contigs", "complete genome", "complete genome", 
                               "contigs", "complete genome", "scaffold"))

library("knitr")
kable(strain, caption = "Table 1. Genomes used in this study.")
```

@@

## Gene Alignment
Gene alignments were in `R` using a ClustalW algorithm. The gene fasta files were read into `R` using the `readDNAStringSet()` function (package: Biostrings) [@Pages2020]. Alignments were done using the `msaClustalW()` function (package: msa) [@Bodenhofer2015] using default parameters and setting maximum number of iterations to 100. The aligned functions were then converted into a readble format using `msaConvert()` (package: msa)[@Bodenhofer2015] and written into a new fasta file using the `write.fasta()` function (package: seqinr) [@Charif2007]

## Distance Matrices
After alignments, model testing was done for each gene through `MEGA-CC` [@Kumar2012] for both nucleotide and amino acid sequences. In a command line terminal, `MEGA-CC` is called along with a text file listing the file pathways to all 799 genes and a MAO file detailling the analysis preferences. Default paramaters were used for model testing. This resulted in a comma-separated values (CSV) file for each gene. These CSV files were read into `R` and the model for phylogenetic analysis was extracted based on lowest Bayesian Information Criterion (BIC). A list of the unique models and the number of genes that required each model are given in Table 2 for nucleotide sequences and in Table 3 for amino acid sequences.

```{r echo = FALSE, message = FALSE, fig.cap=TRUE}
library("tidyverse")

phylo_models_NT <- read.csv("C:/Users/Kim/OneDrive/2020_3Fall/Biology_396/9_Results_NT/Phylo_Models_NT.csv", stringsAsFactors = FALSE)
PM_NT <- data.frame(table(phylo_models_NT$BM))

colnames(PM_NT) <- c("Model", "Number")

PM_NT <- mutate(PM_NT,
             Percent = round((Number / sum(Number)) * 100, digits = 2))

library("knitr")
kable(PM_NT, caption = "Table 2. The number of genes that required each phylogenetic tree model according to model testing and the lowest BIC for nucleotide sequences.")
```

```{r echo = FALSE, message = FALSE, fig.cap=TRUE}

phylo_models_AA <- read.csv("C:/Users/Kim/OneDrive/2020_3Fall/Biology_396/9_Results_AA/Phylo_Models_AA.csv", stringsAsFactors = FALSE)
PM_AA <- data.frame(table(phylo_models_AA$BM))

colnames(PM_AA) <- c("Model", "Number")

PM_AA <- mutate(PM_AA,
                Percent = round((Number / sum(Number)) * 100, digits = 2))

library("knitr")
kable(PM_AA, caption = "Table 3. The number of genes that required each phylogenetic tree model according to model testing and the lowest BIC for amino acid sequences.")
```

@@

# Results and Discussion

# Conclusion

>>>>

---
title: "Untitled"
author: "Kimberly Hinz"
date: "2020/12/08"
output:
  word_document:
    reference_docx: Styles1.docx
    fig_caption: true
    # toc: true
    # toc_depth: 5
bibliography: References.bib
csl: IJSEM.csl
---
```{r Packages, echo = FALSE, message = FALSE, warning=FALSE}
library("knitr")
library("tidyverse")
library("ggplot2")
library("RColorBrewer")
library("extrafont")
theme_set(theme_classic())
```
\newpage
# Abstract
*Mixta* is a recently described genus within the bacterial family *Erwiniaceae* that is closely related to *Pantoea*, *Erwinia*, and *Tatumella*. Depending on the genes and method used for phylogenetic analysis, the genus with which *Mixta* shares the most recent ancestor differs. This study aimed to determine the cause behind these contentious results, and identified genes that may have resulted from horizontal gene transfer. Ten complete or partial genomes – two *Mixta* species, six species from other *Erwiniaceae* genera, and two outgroups – were retrieved from NCBI and annotated. Homologous genes were extracted yielding a dataset of 799 genes. The genes were aligned With the ClustalW algorithm and MEGA-CC was used for model testing and computing phylogenetic trees for each gene for both nucleotide and amino acid sequences. Distance matrices were then extracted from these trees. Nucleotide and amino acid identity analyses were also done in `R` programming language. *Pantoea* was the closest relative to the *Mixta* species in most of the analyses; however, results were not consistent across analyses. Some genes were also found to be more similar to other, non-*Pantoea* species. Diligence must be given to the selection of genes for phylogenetic analysis and to the method chosen to prevent xenologous signal from distorting the true relationships. Furthermore, future research should consider that different phylogenetic analyses may give different results.

@@

```{r Table1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap=TRUE}
strain <- read.csv("C:/Users/Kim/OneDrive/2020_3Fall/Biology_396/10_Tables_and_Figures/Table1_Genomes.csv", stringsAsFactors = FALSE)

kable(strain, caption = "Table 1. Genomes used in this study.")
```

@@

## Gene Alignment
Gene alignments were in `R` using a ClustalW algorithm. The gene fasta files were read into `R` using the `readDNAStringSet()` function (package: Biostrings) [@Pages2020]. Alignments were done using the `msaClustalW()` function (package: msa) [@Bodenhofer2015] using default parameters and setting maximum number of iterations to 100. The aligned functions were then converted into a readable format using `msaConvert()` (package: msa)[@Bodenhofer2015] and written into a new fasta file using the `write.fasta()` function (package: seqinr) [@Charif2007]

## Distance Matrices
After alignments, model testing was done for each gene through `MEGA-CC` [@Kumar2012] for both nucleotide and amino acid sequences. In a command line terminal, `MEGA-CC` is called along with a text file listing the file pathways to all 799 genes and a MAO file detailing the analysis preferences. Default parameters were used for model testing. This resulted in a comma-separated values (CSV) file for each gene. These CSV files were read into `R` and the model for phylogenetic analysis was extracted based on lowest Bayesian Information Criterion (BIC). A list of the unique models and the number of genes that required each model are given in Table 2 for nucleotide sequences and in Table 3 for amino acid sequences.

```{r Table2, echo=FALSE, message=FALSE, warning=FALSE, fig.cap=TRUE}
PM_NT <- read.csv("C:/Users/Kim/OneDrive/2020_3Fall/Biology_396/10_Tables_and_Figures/Table2_PmodelsNT.csv", stringsAsFactors = FALSE)

kable(PM_NT, caption = "Table 2. The number of genes that required each phylogenetic tree model according to model testing and the lowest BIC for nucleotide sequences.")
```

```{r Table3, echo = FALSE, message = FALSE, warning=FALSE, fig.cap=TRUE}
PM_AA <- read.csv("C:/Users/Kim/OneDrive/2020_3Fall/Biology_396/10_Tables_and_Figures/Table3_PmodelsAA.csv", stringsAsFactors = FALSE)

kable(PM_AA, caption = "Table 3. The number of genes that required each phylogenetic tree model according to model testing and the lowest BIC for amino acid sequences.")
```

@@

# Results and Discussion
After the two filters, 799 of of 954 homologous genes remained. The genes included those that encoded rRNA sequences, enzymes, transporters, and housekeeping genes and were scattered across the *M. calida* and *M. gaviniae* genomes.

## Genetic Distance
### Closest Relative
Genetic distance gives a numeric estimate of evolutionary change between species. The species that has the shortest genetic distance to a species of interest is considered to be closest relative. For the following analysis, model testing was done first to estimate the best model for each gene. Next, individual phylogenetic gene trees were created and it was from these that distance matrices were exported. *P. septica* was the closest relative to 66.3% and 66.5% of the *M. calida* and *M. gaviniae* genes, respectively, for the nucleotide sequences (Figure 1). In comparison, only 42.7% and 42.8% of *M. calida* and *M. gaviniae* genes, respectively, are closely related to *P. septica* for the amino acid sequences (Figure 1), but this is still the majority. These results suggest that *P. septica* is the closest relative to *Mixta* followed by *P. agglomerans*. For the amino acid sequences, instead of the *Mixta* genes being more closely related to *P. septica*, they are more closely related to the other species in this study (Figure 1). For example, the percentage of genes related to *P. agglomerans* increased from 13.9% for both of the *Mixta* species to 22.3 and 22.4% to *M. calida* and *M. gaviniae*, respectively. This may be due to a loss of phylogenetic signal when using amino acid sequences as a result of codon degeneracy and having a third of available sites.

```{r Figure1, echo = FALSE, message = FALSE, warning=FALSE, fig.cap="Figure 1. The percentage of genes (out of 799) that were most closely related to any of the eight non-*Mixta* species using genetic distances. The species with the shortest genetic distance from both of the *Mixta* species is considered to be the closest relative. Blue bars are the nucleotide sequences of the genes with light blue bars representing the percentage of *M. calida* genes and dark blue bars representing *M. gaviniae*. Green bars are the corresponding amino acid sequences with light green representing *M. calida* genes and dark blue bars representing *M. gaviniae*. Approximately 66% of *M. calida* and *M. gaviniae* genes were most closely related to *P. septica* when using nucleotide sequences in comparison to only 43% when using amino acid sequences.", fig.width=6.5}
number_relatives <- read.csv("C:/Users/Kim/OneDrive/2020_3Fall/Biology_396/10_Tables_and_Figures/Figure1_FirstRelativeMixtaNTAA.csv", 
                             stringsAsFactors = FALSE) %>%
  mutate(Species = factor(Species, levels = c("P. septica", "P. agglomerans", "E. tasmaniensis", "E. amylovora", "T. ptyseos", "T. saanichensis", 
                                              "E. cloacae", "P. syringae"), ordered = TRUE),
         Type = factor(Type, levels = c("calida_NT", "gaviniae_NT", "calida_AA", "gaviniae_AA"), ordered = TRUE))

ggplot(data = number_relatives, aes(x = Species, y = Percent, fill = Type)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_fill_brewer(palette = "Paired", 
                    labels = c(expression(paste("NT and ", italic("M. calida"), sep = "")), 
                               expression(paste("NT and ", italic("M. gaviniae"), sep = "")), 
                               expression(paste("AA and ", italic("M. calida"), sep = "")), 
                               expression(paste("AA and ", italic("M. gaviniae"), sep = "")))) +
  labs(y = "Percent of Genes", 
       fill = expression(paste("Sequence type and ", italic("Mixta"), " species", sep = ""))) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, face = "italic"),               # Rotates and italicizes x axis labels
        legend.position = c(0.95, 0.95),                                                  # Moves legend inside the plot and in the top-right corner
        legend.justification = c("right", "top"),                                         # Top right corner is at above coordinates
        legend.text.align = 0,                                                            # Aligns legend text to the left
        legend.margin = margin(6, 6, 6, 6),                                               # Margins around legend
        text = element_text(size = 12,  family = "Times New Roman"))
```

Unexpectedly, the number of *Mixta* genes that are more closely related increased from 2.9% to 6.0% when using the amino acid sequences instead of the nucleotide sequences (Figure 1). This, along with the other differences in relatedness for *Mixta* genes between nucleotide and amino acid sequences, suggests that the sequence type used in the analysis will give different results, even when using the same genes.

If genetic distance infers the same closest relative for a *Mixta* gene for both nucleotide and amino acid analyses, then these results may be more reliable. Thus, for genes where the closest relative is an *Erwinia*, *Tatumella*, or *Enterobacter* species both nucleotide and amino acid analyses, they may have resulted from a horizontal gene transfer (HGT) event rather than vertical evolution from a *Pantoea* species. No *Mixta* genes were found to be closely related to *P. syringiae* for either the nucleotide or amino acid sequences (Figure 1). This confirms that *P. syringiae* is a suitable outgroup for this analysis and suggests that any HGT events may be restricted to the order *Enterobacterales*.

### Best Model vs. Best Available Model
In MEGAX [@Kumar2018], the user is restricted to what models can be used when estimating genetic distance; however, the user is not restricted when estimating phylogenetic trees. Model testing in MEGAX tests all of the models that are available for phylogenetic tree analysis. Therefore, the recommended model based on lowest BIC value may not be available for genetic distance analysis. GTR (General Time Reversible) and HKY (Hasegawa-Kishino-Yano) models, as well as the invariant sites (+I) parameter, are not available for genetic distance analysis. In order to determine if the limited options would affect the percentage of each species being the closest relative to the *Mixta* genes, genetic distances were estimated for each gene for the nucleotide sequences in MEGA-CC. The model testing results were filtered to remove the models that are not available for genetic distances in MEGAX and then distance matrices were estimated for each gene using the best available model based on lowest BIC value. As a result, only four of twelve models were available with more than 87% of the genes now using either the Tamura 3-parameter with a Gamma parameter (T92_G) or the Tamura-Nei with a Gamma parameter (TN93_G) (Table 4). This is in comparison to the original 58% of genes that required these models when not restricted by availability. Additionally, the best model was not available for approximately 43% of the genes (242 genes). The mean BIC difference between the best model and the best available model was 2.65 with a range of 0 to 122.6 where 0 means that the best available model is the same as the best model. When ignoring cases where the best available model was also the best recommended model, the mean BIC difference was 13.8 with a range of 0.1 to 122.6. These difference may result in a less accurate estimation of genetic distance between species.

```{r Table4, echo = FALSE, message = FALSE, warning=FALSE, fig.cap=TRUE}
models <- read.csv("C:/Users/Kim/OneDrive/2020_3Fall/Biology_396/10_Tables_and_Figures/Table4_GenDistModelsNT.csv", stringsAsFactors = FALSE)

kable(models, caption = "Table 4. The number of genes requiring each model when using phylogentic tree analysis vs genetic distance analysis in MEGAX for nucleotide sequences.")
```

The closest relatives to both *Mixta* species were extracted from the distance matrices. *P. septica* was estimated to be the closest relative to 12.6 and 14.4% more genes for *M. calida* and *M. gaviniae*, respectively, when the best available models were used (Figure 2). The next largest difference was for genes that were calculated to be most closely related to *P. agglomerans* (Figure 2). Approximately 5.5 and 7.1% less genes were most closely related to *P. agglomerans* when the best available model was used (Figure 2). Additionally, there was more disparity in the closest relatives between *> calida* and *M. gaviniae* when only the best available model was used (Figure 2). When the best model was used, the two *Mixta* typically had the same closest relative for each gene; however, this was the not the case when model options were limited to those available. Due to differences in evolutionary change estimation between models and the addition or exclusion of additional parameters, genetic distances may be inaccurately calculated when the best model is not used and such results may even suggest that sibling taxa are not as closely related as originally hypothesized.

```{r Figure2, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Figure 2. The percentage of genes (out of 799) that were most closely related to any of the eight non-*Mixta* species when using the recommended (best) model from model testing vs the restricted model (best available) options available for genetic distance analysis in MEGAX for nucleotide sequences. The species with the shortest genetic distance from both of the *Mixta* species is considered to be the closest relative. Evolutionary patterns may vary by gene; therefore, it is appropriate to conduct model testing and use the model that explains the most variation. Nevertheless, this model may not be available in some software programs or analysis methods within a software program. Pink bars represent the percentage of *Mixta* genes that are most closely related to any of the non-*Mixta* species when using the recommended model. Orange bars represent the percentage of *Mixta* genes that are most closely related to any of the non-*Mixta* species when using the best available model for genetic distance analysis in MEGAX in which GTR and HKY models and invariant sites parameter are not offered. The lighter shades represent *M. calida* and the darker shades represent *M. gavinaie*.", fig.width=6.5}
number_relatives <- read.csv("C:/Users/Kim/OneDrive/2020_3Fall/Biology_396/10_Tables_and_Figures/Figure2_FirstRelativeBestvsAvailableModelNT.csv", 
                             stringsAsFactors = FALSE) %>%
  mutate(Species = factor(Species, levels = c("P. septica", "P. agglomerans", "E. tasmaniensis", "E. amylovora", "T. ptyseos", "T. saanichensis", 
                                              "E. cloacae", "P. syringae"), ordered = TRUE),
         Type = factor(Type, levels = c("PD_calida", "PD_gaviniae", "GD_calida", "GD_gaviniae"), ordered = TRUE))

ggplot(data = number_relatives, aes(x = Species, y = Percent, fill = Type)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_fill_manual(values = c("#fb9a99", "#e31a1c", "#fdbf6f", "#ff7f00"),
                    labels = c(expression(paste("Best Model and ", italic("M. calida"), sep = "")), 
                               expression(paste("Best Model and ", italic("M. gaviniae"), sep = "")), 
                               expression(paste("Best Available Model and ", italic("M. calida"), sep = "")), 
                               expression(paste("Best Available Model and ", italic("M. gaviniae"), sep = "")))) +
  labs(y = "Percent of Genes", 
       fill = expression(paste("Model and ", italic("Mixta"), " species", sep = ""))) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, face = "italic"),               # Rotates and italicizes x axis labels
        legend.position = c(0.95, 0.95),                                                  # Moves legend inside the plot and in the top-right corner
        legend.justification = c("right", "top"),                                         # Top right corner is at above coordinates
        legend.text.align = 0,                                                            # Aligns legend text to the left
        legend.margin = margin(6, 6, 6, 6),                                               # Margins around legend
        text = element_text(size = 12,  family = "Times New Roman"))
```

When the closest relative results were compared between when using the best model vs when using the best available, about 20.0 and 22.3% of *M. calida* and *M. gaviniae* genes were estimated to have a different closest relative. Thus, for 82 *M. calida* genes and 64 *M. gaviniae* genes, the same closest relative was called despite using a different model. This may because the best model and the best available for those genes were similar and explained approximately the same amount of variance.

Each model estimates genetic distance differently. The best model explains most of the variance between sequences and gives a more accurate estimation of genetic distance. Using a model that does not explain most of the variance between sequences will estimate genetic distance less accurately which may result in related taxa (such as those from the same species) having a longer genetic distance between them than in actuality. This may also result in the opposite for taxa that are not closely related (i.e. *Pantoea* spp. and *E. cloacae*). Even though only two of the nucleotide models and one parameter were unavailable for genetic distance analysis in MEGAX, the results for closest relative to *Mixta* genes was substantially impacted. This was particularly the case between the two *Mixta* as one would expect them to have the same closest relative for most of the homologous genes. Therefore, using the best model is recommended. However, this may not be possible when estimating genetic distance using more than one gene that may require different models. Thus, it must be considered that one or more the genes in the concatenation may have a different evolutionary pattern than the others and results should be investigated further to ensure accuracy.

Even though genetic distance estimation in MEGAX did not offer all of the models and parameters as suggested by model testing, all of the models and parameters were available for phylogentic tree analysis and genetic distance can be exported from these trees. However, this has to be done manually by opening the tree file in MEGAX and exporting the distance matrix as either an Excel or CSV file and is therefore not feasible when hundreds or thousands of genetic distance matrices are needed.

### Spatial Patterns of Closest Relatives
To assess whether there were any positional effects of the genes and spatial patterns of the closest relatives, circular plots were generated using the *Mixta* gene IDs for nucleotide sequences (Figure 3) and amino acid sequences (Figure 4). The gene IDs give the approximate location of each gene relative to the *Mixta* genome. The length and colour of a bar represents the species that was the closest relative to the *Mixta* gene at that position. Since the closest relatives were the same both *Mixta* species except for 1 and 2 genes for nucleotide and amino acid sequences, respectively, only the results for *M. calida* are shown. These genes will be discussed later on.

The genes showing greatest identity (lowest distance) to P. septica are distributed across the genome for both M. calida and M. gaviniae (Figures 1 and 2), further suggesting Mixta and Pantoea species have a recent common ancestor. If many genes were horizontally transferred in a single event, then large blocks of genes from a single species would be expected. However, the Erwinia lines (green) are fairly even throughout the genome and the outgroup lines (red and orange) are separated with genes in between. This suggests that Mixta underwent many HGT after speciation from Pantoea.

Positional effects of all of the species and range of the distances were also evaluated (Figures 3 and 4). For most genes, the genetic distance for each of the eight species ranged from 0 to 1.5 with only a few greater than 2. The cluster of genes around ID 425 in both M. calida and M. gaviniae have a very small range and so are highly conserved among all of the species. These genes were annotated as being ribosomal genes. Furthermore, Pantoea species (blue dots) are typically the closest relative to Mixta, followed by Erwinia (green). The Tatumella species (purple and pink) and the outgroup species (red and orange) vary as to which are the furthest relative to Mixta.

```{r Figure3, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Figure 3.", fig.width=6.5, fig.height=5}
FR_nucl_calida <- read.csv("C:/Users/Kim/OneDrive/2020_3Fall/Biology_396/10_Tables_and_Figures/Figure3_Circular_NT.csv", stringsAsFactors = FALSE) %>%
  mutate(Closest_Relative = factor(Closest_Relative, 
                                   levels = c("P_septica", "P_agglomerans", "E_tasmaniensis", "E_amylovora", "T_ptyseos", 
                                              "T_saanichensis", "E_cloacae", "P_syringiae"), ordered = TRUE))

ggplot(FR_nucl_calida, aes(x = ID, y = Relative_Number, fill = Closest_Relative)) +
  geom_bar(stat = "identity", position = position_dodge(), width = 15) +
  coord_polar() +
  scale_fill_brewer(palette = "Paired", 
                    labels = c("P. septica", "P. agglomerans", "E. tasmaniensis", "E. amylovora", "T. ptyseos", "T. saanichensis", "E. cloacae",
                               "P. syringiae")) +
  scale_y_continuous(limits = c(0, 9), breaks = c(0, 2, 4, 6, 8)) +
  labs(fill = "Closest Relative") +
  theme_bw() +
  theme(legend.text = element_text(face = "italic"),
        axis.title = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        text = element_text(size = 12,  family = "Times New Roman"))
```

```{r Figure4, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Figure 4.", fig.width=6.5, fig.height=5}
FR_aa_calida <- read.csv("C:/Users/Kim/OneDrive/2020_3Fall/Biology_396/10_Tables_and_Figures/Figure4_Circular_AA.csv", stringsAsFactors = FALSE) %>%
  mutate(Closest_Relative = factor(Closest_Relative, 
                                   levels = c("P_septica", "P_agglomerans", "E_tasmaniensis", "E_amylovora", "T_ptyseos", 
                                              "T_saanichensis", "E_cloacae", "P_syringiae"), ordered = TRUE))

ggplot(FR_aa_calida, aes(x = ID, y = Relative_Number, fill = Closest_Relative)) +
  geom_bar(stat = "identity", position = position_dodge(), width = 15) +
  coord_polar() +
  scale_fill_brewer(palette = "Paired", 
                    labels = c("P. septica", "P. agglomerans", "E. tasmaniensis", "E. amylovora", "T. ptyseos", "T. saanichensis", "E. cloacae",
                               "P. syringiae")) +
  scale_y_continuous(limits = c(0, 9), breaks = c(0, 2, 4, 6, 8)) +
  labs(fill = "Closest Relative") +
  theme_bw() +
  theme(legend.text = element_text(face = "italic"),
        axis.title = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        text = element_text(size = 12,  family = "Times New Roman"))
```

Nucleotides: ttuB where M. calida is with T. ptyseos and M. gaviniae is with P. septica
Amino acids: ttuB where M. calida is with T. saanichensis and M. gaviniae is with P. septica 
             secY where M. calida is with E. tasmaniensis and M. gaviniae is with P. agglomerans
# Conclusion
